Confocal Raman Thermometer for Microfluidic Devices

### 2018-10-19 paper.tex
casa. Agrego parte experimental

>>>>

\section{Experimental}

The setup used to measure the temperature in the microchannels is depicted in fig. 1. The device works as a confocal microscope, where the traditional pinhole is replaced with a multimode optical fiber. The excitation beam is a 150mW laser diode emitting at a wavelength of 405 nm. The beam is spatially filtered using a single mode optical fiber to achieve a nearly gaussian spatial mode before entering the microscope. To achieve a tighter focus at the sample plane a 3.6X telescope is used to increase beam waist after the spatial filter. At this point, a longpass dicroic mirror splitting in 420 nm is used to reflect the excitation beam in the direction of the sample. The beam then reflects in a second dicroic mirror centered around 500 nm and then is focused on the sample using a 40X, 0.95 NA microscope objective. The final optical power at the sample is 25 mW at 405 nm. The backscattered Raman emission of the sample is collected by the same microscope objective and directed to the optical fiber. As the Raman spectrum of water is centered around 470 nm, the signal beam will reflect in the first dicroic mirror (500 nm cutoff) and then transmit on the second (420 nm cutoff). After that, the light is directed to the multimode optical fiber by using two mirrors. A 10X, 0.28 NA microscope objective is used to focus the beam in the optical fiber which is mounted in a 3 axis micrometric linear translation stage. This allows a confocal collection volume of … with a lateral resolution of … and an axial resolution of … . The sample is mounted in a platform with tree motorized linear degrees of freedom (xyz) and two manually controlled angular (pitch and yaw) degrees of freedom used to place the sample parallel to the detection plane. This allows the device to make three dimensional temperature maps of the sample. A galvo mirror scanning scheme is also possible to achieve higher spatial resolution imaging but the resolution provided by the motorized stage (312 nm lateral, 82 nm vertical) was exceedingly good for the samples studied in this paper.

 At the same time Raman measurements are being performed a longer wavelength can be used to get a fluorescence or scattering image of the sample. With this purpose a 10 mW laser beam at 520 nm is used to illuminate the sample in an angle greater than the collection angle of the objective (71.8 $\deg$ for a 0.95 NA objective). The scattered light or the emitted fluorescence is then collected and separated from the Raman beam using the first dicroic mirror which is transparent at these wavelengths. Then, a 100 mm tube lens is used to get an image of the sample plane at a CCD camera (Pixelink model). Using this method an image of the sample can be achieved without interfering with the Raman measurements. This can be used to select a particular place in the sample to perform the temperature measurements or to monitor the fluid motion if fluorescent particles are added to the studied fluid. In the latter case a longpass optical filter should be placed before the camera to eliminate any scattering component at the laser wavelength. If this method is performed, care must be taken in the type and concentration of the particles used, as an undesired fluorescence signal might be excited by the 405 nm beam and collected in the Raman channel if it passes through the confocal volume. But, as the latter is designed to be small, at low particle concentrations the probability of such event can be small enough to not interfere with the temperature measurements. Also, as the Raman cross section of water is low, the contribution to the total signal in the Raman channel of a fluorescent particle passing rapidly through the confocal volume is a sharp peak which can be easily filtered of the temperature signal which is generally expected to be smooth.

At the other end of the multimode optical fiber the Raman signal beam is divided in the two spectral bands necessary for the temperature measurement and then detected. For this purpose a transmission diffraction grating (300 l/mm) and a 200 mm achromatic lens is used as a simple spectrometer. A D shaped mirror is used in the lens focal plane to separate the two spectral bands. The latter is mounted in a micrometric translation stage which allows a fine tunning of the separation wavelength which must be matched to the isosbectic point in order to maximize the temperature sensitivity of the method. After this both reflected and transmited beam are directed to the detectors. A 75 mm lens is used in each path to make a one on one image of the D shaped mirror plane in each detector. These ones are two photon counting modules (Hamamatsu model) providing a quantum efficiency of around 15\%. The devices are designed to produce a pre amplified and shaped square pulse for each detected photon simplifying the photon counting procedure. The pulses are then counted in a selectable time window using an on board DAQ device on a PC. Counting rates of around … are achieved at each channel. After this, the final signal is computed at software level as
\begin{equation}\label{eq:senal}
S = \frac{B – A}{A + B}
\end{equation}
where A and B are the counts of each channel. The temperature of the sample is obtained from this calculation after proper calibration.  It is important to notice that $S$ is computed as a ratio, making the calibration independent of experimental parameters such as the excitation power or the integration time.

Additionally the diffraction grating is mounted in a motorized rotation stage.  This is not completely necessary to the Raman measurements but allows using the device as a spectrometer by measuring the signal as a function of the incidence angle on the grating and then taking the numeric derivative of the data. This simplifies the procedure of choosing the isosbectic point and allows checking the detected spectrum to match the one of water, confirming the proper alignment of the microscope.

As the detectors are very sensitive and the Raman signal is very low, the whole detection part of the setup is enclosed in an opaque box to avoid ambient light reaching the detectors. This is a great advantage of using an optical fiber to produce the confocal resolution instead of a pinhole as the ambient light coupled to the fiber is practically null and the signal beam can be conveniently directed to the enclosed part of the setup, allowing a much relaxed illumination constrain in the laboratory.

To calibrate the method a temperature controlled water cell was used. This was constructed using a rectangular aluminum plate with a perforation sealed with two glass windows and containing around 150 ul of distilled water. A peltier cell was fixed at one side of the piece to achieve either heating or cooling and a thermistor is used to monitor the piece temperature.  Placing this cell in the sample plane of the microscope allows a temperature controlled water sample used to set the isosbestic point and to calibrate the method. 
Aca iria un parrafo contando las caracteristicas de los microcanales que usamos como muestra (tal vez convenga pedirle a Martin que lo escriba o que nos diga que es relevante decir sobre el proceso con el que los armo). Cosas que pienso que van: que están pegados a cubres de 150 um. Que se uso KCl para setear la conductividad en 5000 mS/cm. Las medidas de los canales. Que se alimento con una fuente de tensión regulable de hasta 1kV logrando los campos eléctricos …

\section{Results}
Va algo de la caracterización de la resolucion lateral/ axial?
The calibration of the method was obtained by using the temperature controlled cell and by computing the $S$ from the readings obtained from each detector as described in equation \ref{eq:senal}. In figure \ref{fig:calibracion} a calibration is shown where the value of $S$ is plotted for different temperatures. A linear dependence is exhibited in the range of interest, resulting in a simple calibration. After this is done, the temperature resolution of the method can be estimated by measuring the noise in the temperature signal at a given temperature and integration time. This is achieved by measuring the temperature multiple times and computing the standard deviation of the obtained data. Using this method, a temperature resolution of 0.8 K was measured with an integration time of one second. This result is similar to the obtained by computing the dispersion of the data around the linear fit in the calibration.
Using this calibration the temperature rise in the microchannels was measured at its center as a function of the power dissipated on it and horizontal, vertical and axial profiles were measured at fixed power. This allows fully characterizing the dissipation mechanism in the channels as the heat flow is proportional to the spatial temperature gradient as stated by Fourier’s law. A simple model can be made by considering one by one each dissipation mechanism and by computing the required spatial temperature gradient to achieve a stationary temperature. The path with the lowest temperature gradient is the most likely to dominate heat flow in the channel. Con que detalle se hacen estas cuentas?
